---
title: "Weight of Fish"
author: "Christina Jones"
date: "Fall 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
fish <- read.csv("Fish.csv")
```




# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Build the best regression model to predict the weight of Perch, Pike and Roach that uses two predictor variables. We are trying to find the best two variable to predict weight of each type of fish. 

## Build the best regression model you can that predicts the weight of Perch
## Using only two predictor variables  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Subset of fish that contains the species you want to analyze and then I will look at how well each combination of the predictor variables can predict the weight of a fish. The PERCH will be the first species of fish.  

```{r}
Perch = filter(fish, Species=="Perch")
```

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
basicNN <- ggplot(Perch,aes(y=Weight,x=Length1))
```

```{r}
basicNN + geom_point()
```
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

On the Y axis weight is represented and on the x axis length1 is represented. As the length1 increases so does the weight of the Perch fish. The blue line represents the regression between the two variables. 

### Numerical Descriptive Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = select (Perch, -Species),
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
fullup=lm(Weight~.,data=select(Perch,-Species))
```
Using this model using all the variables, Perch fish weight can better be predicted when using Height of the fish. 


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$ The models show no difference in the prediction of weight Perches.

$H_A$ The models help with predicting the weight of Perches. 


```{r}
anova(fullup,best.model)
```
We failed to reject the null hypnosis when the p value is above 0.005. The P value is 0.879 which is much larger then 0.005. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Using all the variables to come up the best way to predict the weight of Perches. It is concluded the Height is the best predictor for Perches Weight. 

The second fish i will predict is the Pike. 


```{r}
Pike =filter(fish, Species=="Pike")
```


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicNN <- ggplot(Pike,aes(y=Weight,x=Length1))
```

```{r}
basicNN + geom_point()
```
```{r}
basicNN + geom_point()+geom_smooth(method=lm)
```
On the Y axis weight is represented and on the x axis length1 is represented. As the length1 increases so does the weight of the Pike. The blue line represents the regression between the two variables. 



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = select (Perch, -Species),
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
which.max(summary.out$adjr2)
```

```{r}
best.model <- lm(Weight~Height+Width,data=Pike)
summary(best.model)
fullup=lm(Weight~.,data=select(Pike,-Species))
```
Using this model using all the variables, Pike fish weight can better be predicted when using Height of the fish. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$ The models show no difference in the prediction of weight Pikes.

$H_A$ The models help with predicting the weight of Pikes. 

```{r}
anova(fullup,best.model)
```

We failed to reject the null hypnosis when the p value is above 0.005. The P value is 00000 which is much larger then 0.005. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Using all the variables to come up the best way to predict the weight of Pikes. It is concluded the Height is the best predictor for Pikes Weight.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


